An introduction to lightlabsFDS

### 2012-03-01 presentations/lightlabsFDS_mar-2012/pres.tex
Final presentation (group meeting).

\BIT \itemsep -1pt
\I  The lightlabsFDS mission
\I  Solver
\I  Interface
\I  Hardware
\I  End it
\EIT

@@

% \begin{center}
\begin{pspicture}(6,5)(-6,0)
    \psgrid

@@

    \pspolygon[fillcolor=lightgray,fillstyle=solid]
        (2.4,4)(2.4,1)(3.2,0.5)(3.2,4.5)
    \psline(4,4)(3.2,4) \rput(4.8,4){$Y(\omega_1)$}
    \psline(4,3)(3.2,3) \rput(4.8,3){$Y(\omega_2)$}
    \psline(4,2)(3.2,2) \rput(4.8,2){$\vdots$}
    \psline(4,1)(3.2,1) \rput(4.8,1){$Y(\omega_n)$}
\end{pspicture}
% \end{center}
\BIT
\I  Fundamental problem: trying to use a time-domain solver as a 
        frequency-domain solver.
\I  Additionally, no method to measure simulation error!
\EIT
\newpage

\begin{center}
\begin{pspicture}(6,4)(-6,-2)
    \psgrid

@@

    \psframe[fillstyle=none](-1,-0.4)(1,-1.4)
    \rput(0,-0.9){\textrm{FDS}}
    \psline(-2.4,-0.9)(-1,-0.9)
    \rput(-3.2,-0.9){$X(\omega_n)$}
    \psline(2.4,-0.9)(1,-0.9)
    \rput(3.2,-0.9){$Y(\omega_n)$}
\end{pspicture}
\end{center}
\BIT
\I  Allow direct access to frequency-domain data.
\I  Take care of input and output fields outside of the simulation.
\I  Material dispersion explicitly defined.
\I  Simulation error well defined.
\EIT
\newpage

\begin{center}
% \includegraphics[width=\textwidth]{pml_cutout}
\end{center}
\BIT
\I  Frequency-domain solver made possible by correct choice of PML and 
        linear algebra algorithm.
\I  See: Wonseok Shin, Shanhui Fan, 
            ``Choice of the perfectly matched layer boundary condition for 
            frequency-domain Maxwell's equations solvers'',
            Journal of Computational Physics (January 2012).
\EIT

@@

\oursection{Hardware}
\begin{center}
\begin{pspicture}(6,3)(-6,-3)
    \psgrid
    \rput(0,0){\parbox{5cm}{\begin{center}\textrm{lightlabsFDS\\server}
                            \end{center}}}
    \psline{<->}(-1.2,0.8)(-2.8,1.4) \rput(-3.5,1.5){\textrm{user1}}
    \psline{<->}(-3.2,0)(-1.6,0) \rput(-4,0){\textrm{user2}}
    \psline{<->}(-1.2,-0.8)(-2.8,-1.4) \rput(-3.5,-1.5){\textrm{user3}}
    \psline{<->}(1.2,0.8)(2.8,1.4) \rput(3.5,1.5){\textrm{user4}}
    \psline{<->}(3.2,0)(1.6,0) \rput(4,0){$\vdots$}
    \psline{<->}(1.2,-0.8)(2.8,-1.4) \rput(3.5,-1.5){\textrm{userN}}
\end{pspicture}
\end{center}
\BIT
\I  Centralized, shared, custom-tuned server able to deliver the performance
        of a large cluster
\I  Performance achieved via heavily optimized GPU code
\I  Multiple servers can be clustered with nearly $100\%$ computational
        efficiency.
\EIT

>>>>

\BIT \itemsep -1pt
\I  The lightlabsFDS mission
\I  Solver
\I  Interface
\I  Hardware
\I  Current status 
\EIT

@@

\begin{center}
\begin{pspicture}(6,5)(-6,0)
    \let\psgrid\relax

@@

    \pspolygon[fillcolor=lightgray,fillstyle=solid]
        (2.4,4)(2.4,1)(3.2,0.5)(3.2,4.5)
    \psline(4,4)(3.2,4) \rput(4.8,4){$Y(\omega_1)$}
    \psline(4,3)(3.2,3) \rput(4.8,3){$Y(\omega_2)$}
    \psline(4,2)(3.2,2) \rput(4.8,2){$\vdots$}
    \psline(4,1)(3.2,1) \rput(4.8,1){$Y(\omega_n)$}
\end{pspicture}
\end{center}
\BIT
\I  Fundamental problem: trying to use a time-domain solver as a 
        frequency-domain solver.
\I  Additionally, no method to measure simulation error!
\EIT
\newpage

\begin{center}
\begin{pspicture}(6,4)(-6,-2)
    \let\psgrid\relax

@@

    \psframe[fillstyle=none](-1,-0.4)(1,-1.4)
    \rput(0,-0.9){\textrm{FDS}}
    \psline(-2.4,-0.9)(-1,-0.9)
    \rput(-3.2,-0.9){$X(\omega_n)$}
    \psline(2.4,-0.9)(1,-0.9)
    \rput(3.2,-0.9){$Y(\omega_n)$}
\end{pspicture}
\end{center}
In contrast, a frequency-domain solver allows
\BIT
\I  Direct access to frequency-domain data,
\I  External processing of input and output fields,
\I  Explicit definition of material dispersion, and
\I  Explicit measurement of simulation error.
\EIT
\newpage

\begin{center}
\includegraphics[width=0.8\textwidth]{pml_cutout}
\end{center}
\BIT
\I  Frequency-domain solver made possible by correct choice of PML and 
        linear algebra algorithm.
\I  See: Wonseok Shin, Shanhui Fan, 
            ``Choice of the perfectly matched layer boundary condition for 
            frequency-domain Maxwell's equations solvers'',
            Journal of Computational Physics (January 2012).
\EIT

@@

\oursection{Hardware}
\begin{center}
\begin{pspicture}(6,3)(-6,-3)
    \let\psgrid\relax
    \rput(0,0){\parbox{5cm}{\begin{center}\textrm{lightlabsFDS\\server}
                            \end{center}}}
    \psline{<->}(-1.2,0.8)(-2.8,1.4) \rput(-3.5,1.5){\textrm{user1}}
    \psline{<->}(-3.2,0)(-1.6,0) \rput(-4,0){\textrm{user2}}
    \psline{<->}(-1.2,-0.8)(-2.8,-1.4) \rput(-3.5,-1.5){\textrm{user3}}
    \psline{<->}(1.2,0.8)(2.8,1.4) \rput(3.5,1.5){\textrm{user4}}
    \psline{<->}(3.2,0)(1.6,0) \rput(4,0){$\vdots$}
    \psline{<->}(1.2,-0.8)(2.8,-1.4) \rput(3.5,-1.5){\textrm{userN}}
\end{pspicture}
\end{center}
\BIT
\I  Centralized, shared, custom-tuned server able to deliver the performance
        of a large cluster
\I  Performance achieved via heavily optimized GPU code
\I  Multiple servers can be clustered with nearly $100\%$ computational
        efficiency.
\EIT
